---
title: "CE_Model"
author: "Sarah Klain"
date: "October 23, 2015"
output: 
  html_document: 
    keep_md: yes
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
setwd("/Users/sarahklain/Documents/R_2015/wf_ce/CE")

library(ggplot2)
library(ggthemes)
library(wesanderson)
library(viridis)
suppressMessages(library(dplyr))
library(knitr)
library(tidyr)
library(broom)
#install.packages("support.CEs")
library(support.CEs)
# install.packages("xlsx")
library(xlsx)
library(survival)
library(mlogit)
```

load choice experiment responses data


Figure out how the data should be formatted if I had used a rotational design.

```{r}
des1 <- rotation.design(
  attribute.names = list(
    hab_qual = c("big loss", "small loss", "small gain", "big gain"), 
    own = c("state", "municipal", "private", "cooperative"), 
    vis = c("mi1", "mi4", "mi8", "mi10"), 
    bill  = c("1", "5", "10", "20")), 
  nalternatives = 2,
  nblocks = 4,
  row.renames = FALSE, 
  randomize = TRUE,
  seed = 987)

des1
```

lma design
```{r}
des_lma <- Lma.design(
     attribute.names = list(
       hab_qual = c("big loss", "small loss", "small gain", "big gain"), 
       own = c("state", "municipal", "private", "cooperative"),
       vis = c("mi1", "mi4", "mi8", "mi10"), bill = c("1", "5", "10", "20")), 
       nalternatives = 2,
       nblocks = 4, 
       row.renames = FALSE,
       seed = 987)

des_lma
```

The format for the design matrix

rotational design

```{r}
desmat1 <-make.design.matrix(
  choice.experiment.design = des1,
  optout = TRUE,
  categorical.attributes = c("hab_qual", "own", "vis"), 
  continuous.attributes = c("bill"),
  unlabeled = TRUE)

desmat1
write.xlsx(desmat1, "desmat1.xlsx")
```



```{r}
desmat_lma <-make.design.matrix(
  choice.experiment.design = des_lma,
  optout = TRUE,
  categorical.attributes = c("hab_qual", "own", "vis"), 
  continuous.attributes = c("bill"),
  unlabeled = TRUE)

desmat_lma
write.xlsx(desmat_lma, "desmat_lma.xlsx")
```

manually match my JMP CE configuration to the desmat1 format
```{r}
desmat2 <- read.xlsx("desmat2", 1)

```

The R CE package did not include the the first level of each attribute. I manually insterted it into the excel sheet, then copy and pasted as values. 

```{r}
desmat3 <- read.csv("desmat3.csv")
#delelted first in each attribute type

desmat4 <- read.csv("desmat4.csv")
str(desmat4)
str(desmat1)
```


```{r}
str(desmat3)
```

```{r}
cer <- read.csv("cer_2015_10_23_min.csv")
cer_big <- read.csv("cer_2015_10_23.csv")

str(cer)
```

This function makes a data set used for a conditional logit model analysis with the function clogit in the package survival or for a binary choice model analysis with the function glm in the package stats.

make.dataset(respondent.dataset, design.matrix,
                 choice.indicators, detail = FALSE)

 choice.indicators = 
  c("q1", "q2", "q3", "q4", "q5", "q6", "q7", "q8", "q9"), 
 design.matrix = desmat2)
```{r}
#str(cer)
#check cer!

#desmat5 <- read.csv("desmat5.csv")

desmat4 <- read.csv("desmat4.csv")

head(desmat4)
ds <- make.dataset(respondent.dataset = cer, design.matrix = desmat_lma, choice.indicators = c("q1", "q2", "q3", "q4", "q5", "q6", "q7", "q8"), detail = TRUE)

ds

ds2 <- make.dataset(respondent.dataset = cer, design.matrix = desmat4, choice.indicators = c("q1", "q2", "q3", "q4", "q5", "q6", "q7", "q8"), detail = TRUE)

ds2
```


Examples
```{r}
d.pork <- Lma.design(
  attribute.names = list(
    Price = c("100", "130", "160", "190")),
  nalternatives = 3,
  nblocks = 4,
  row.renames = FALSE,
  seed = 987)
dm.pork <- make.design.matrix(
  choice.experiment.design = d.pork,
  optout = TRUE,
  continuous.attributes = c("Price"),
  unlabeled = FALSE)


data(pork)
ds.pork <- make.dataset(
  respondent.dataset = pork,
  choice.indicators =
    c("q1", "q2", "q3", "q4"),
  design.matrix = dm.pork)
fm.pork <- RES ~ ASC1 + Price1 +
  ASC2 + Price2 +
  ASC3 + Price3 +
  strata(STR)
out.pork <- clogit(fm.pork, data = ds.pork)
out.pork

####

des2 <- Lma.design(
  attribute.names = list(
    Eco = c("Conv.", "More", "Most"),
    Price = c("1", "1.1", "1.2")),
  nalternatives = 3,
  nblocks = 2,
  row.renames = FALSE,
  seed = 987)
des2
questionnaire(choice.experiment.design = des2, quote = FALSE)
desmat2 <- make.design.matrix(
  choice.experiment.design = des2,
  optout = TRUE,
  categorical.attributes = c("Eco"),
  continuous.attributes = c("Price"),
  unlabeled = FALSE)


data(syn.res2)
dataset2 <- make.dataset(
  respondent.dataset = syn.res2,
  choice.indicators =
    c("q1", "q2", "q3", "q4", "q5", "q6", "q7", "q8", "q9"),
  design.matrix = desmat2)

head(dataset2)
dim(dataset2)
```
LMA 

```{r}

###
des3 <- Lma.design(
 attribute.names = list(
  Region = c("Reg_A", "Reg_B", "Reg_C"),
  Eco = c("Conv.", "More", "Most"),
  Price = c("1", "1.1", "1.2")),
 nalternatives = 1,
 nblocks = 1,
 row.renames = FALSE,
 seed = 987)
des3
questionnaire(choice.experiment.design = des3, quote = FALSE)
desmat3 <- make.design.matrix(
 choice.experiment.design = des3,
 optout = TRUE,
 categorical.attributes = c("Region", "Eco"),
 continuous.attributes = c("Price"),
 unlabeled = TRUE,
 common = NULL,
 binary = TRUE)
data(syn.res3)
dataset3 <- make.dataset(
 respondent.dataset = syn.res3,
 choice.indicators =
  c("q1", "q2", "q3", "q4", "q5", "q6", "q7", "q8", "q9"),
 design.matrix = desmat3)
blout <- glm(RES ~ Reg_B + Reg_C + More + Most + Price,
 family = binomial(link = logit), data = dataset3)
summary(blout)
gofm(blout)
mwtp(output = blout,
 monetary.variables = c("Price"),
 nonmonetary.variables =
  c("Reg_B", "Reg_C", "More", "Most"),
 seed = 987)
```



