---
title: "WF_data_explore"
author: "Sarah Klain"
date: "October 14, 2015"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Wind Farm Data Cleaning and Exploration

### Data Cleaning
I deleted the following columns:

ResponseSet
Name
ExternalDataReference
EmailAddress
Status

I deleted incomplete surveys
I made ethnic origin one column
Attention filter: if att1 = 0 and att2 = 5 then I deleted row

```{r}
install.packages("support.CEs")
library(support.CEs)
library(ggplot2)
library(ggthemes)
library(wesanderson)

w <- read.csv("~/Documents/R_2015/wf_ce/Coded_WF_10_14_2015.csv")
str(w)
summary(w)
head(w)
```

Plots of data by demographic variables
```{r}
inc <- ggplot(w, aes(x = income))
inc + geom_histogram(binwidth=1) + 
  xlab("Income") + ylab("Count")

gen <- ggplot(w, aes(x = gender))
gen + geom_histogram() + theme_pander() +
  xlab("Gender") + ylab("Count") + scale_x_discrete(breaks=c(1, 2))

pol <- ggplot(w, aes(x = pol))
pol + geom_bar() +
  xlab("Political Party") + ylab("Count")

emp <- ggplot(w, aes(x = employ))
emp + geom_histogram() +
  xlab("Employment") + ylab("Count")

age <- ggplot(w, aes(x = age))
age + geom_histogram(binwidth = 3) +
  xlab("Age") + ylab("Count")

```
## Constructed Means

Input data
```{r}
cm <- read.csv("~/Documents/R_2015/wf_ce/Constr_means_MT.csv")
str(cm)
summary(cm)
head(cm)
```

I did exploratory plots of the data

```{r}
ggplot(cm, aes(x = type_mean, y = con_mean)) +
  geom_jitter(position = position_jitter(width = 0.04, height = 0), color = "goldenrod1", alpha = 1/5) +
  stat_summary(fun.y = min, colour = "turquoise4", geom = "point", size = 4) +
  stat_summary(fun.y = max, colour = "red3", geom = "point", size = 4) +
  geom_boxplot(width=.2, outlier.shape = NA, alpha = 0.1) +
  xlab("Type of Constructed Mean") + ylab("Mean Level of Agreement")
```
And a squiggly violin plot! 
```{r}
ggplot(cm, aes(x = type_mean, y = con_mean)) +
  geom_jitter(position = position_jitter(width = 0.04, height = 0), color = "goldenrod1", alpha = 1/5) +
  stat_summary(fun.y = min, colour = "turquoise4", geom = "point", size = 4) +
  stat_summary(fun.y = max, colour = "red3", geom = "point", size = 4) +
  geom_violin(alpha = 0.1) +
  xlab("Type of Constructed Mean") + ylab("Mean Level of Agreement")
```