---
title: "CE_mlogit"
author: "Sarah Klain"
date: "November 20, 2015"
output: 
  html_document: 
    keep_md: yes
---

```{r}
setwd("/Users/sarahklain/Documents/R_2015/wf_ce/CE/demog")

#install.packages("support.CEs")
library(ggplot2)
library(ggthemes)
library(viridis)
suppressMessages(library(dplyr))
library(knitr)
library(tidyr)
library(broom)
#library(support.CEs)
library(survival)
library(mlogit)
library(stargazer)
```


Follow along Viton's work
Conditional Logistic Regression
```{r}
#clogit <- read.csv("clogit.csv", na.strings= "-999")

# read in the data
library(foreign)
clogit <- read.csv("clogit.csv", col.names=c("mode","ttme","invc","invt","gc","chair","hinc", "psize","indj","indi","aasc","tasc","basc","casc","hinca","psizea","z","nij","ni"),na.strings="-999")
 
# check the data
summary(clogit)
str(clogit)
head(clogit)
# save a version of the data in internal format
save(clogit,file="clogit.rdata")
# read in the mlogit package
library(mlogit)
# read in the data we saved
load(file="clogit.rdata")
# provide a choice indicator, with names
clogit$mode.ids<-factor(rep(1:4,210),labels=c("air","train","bus","car"))

# for convenience, create a special form of the dataset: note that we exploit the case sensititivty here: clogit is the original dataset, while CLOGIT (all-caps) is the version for use with the mlogit package.

CLOGIT<-mlogit.data(clogit,shape="long",choice="mode",alt.var="mode.ids")

# first model : standard logit. We save the results into a variable and then view them. The first command uses the un-fixed dataset, while the second uses the mlogit-specific dataset, and is clearly easier to type in. Both produce the same output.

res1<-mlogit(mode~ttme+gc, data=clogit, shape="long",
                alt.var="mode.ids")
summary(res1)
res2<-mlogit(mode~ttme+gc,data=CLOGIT)
summary(res2)

# model with income interacted with the mode-specific dummys
res3<-mlogit(mode~ttme+gc | hinc, data=CLOGIT)
summary(res3)

 # model with gc arying by mode
res4<-mlogit(mode~ttme | hinc | gc, data=CLOGIT)
summary(res4)

# mixed logit model  in which the alt-specific vars have independent normal distributions. We use Halton numbers for efficiency in computation, and use R=500 in our simulationsnote that the syntax for specifying random alt-specific dummys has changed.
# we set print.level to 1 to get some feedback

res5<-mlogit(mode~ttme+gc,data=CLOGIT,reflevel="car",
      rpar=c("air:(intercept)"="n","bus:(intercept)"="n",
      "train:(intercept)"="n"),R=500,halton=NA,print.level=1)
summary(res5)

# print info on what was estimated for a random parameter
rpar(res5,"air:(intercept)")

# same model, but multinomial probit (not discussed in the text)
res6<-mlogit(mode~ttme+gc,data=CLOGIT,reflevel="car",
             R=500,halton=NA,probit=TRUE,print.level=1)
summary(res6)
# Omega-sub-i for each mode:
res6$omega
```

Learn from the examples of Croissant (2011).
```{r}
library("mlogit")
data("Train", package = "mlogit")
head(Train, 3)
Tr <- mlogit.data(Train, shape = "wide", choice = "choice", varying = 4:11, sep = "", alt.levels = c(1, 2), id = "id")
head(Tr, 3)
head(index(Tr), 3)

#change price and time to more meaningful units (euros, hours respectively)
Tr$price <- Tr$price/100 * 2.20371
Tr$time <- Tr$time/60

#We then estimate the model: both alternatives being virtual train trips, it is relevant to use only generic coefficients and to remove the intercept:

ml.Train <- mlogit(choice ~ price + time + change + comfort | -1, Tr)
summary(ml.Train)

#coefficients are not directly interpretable, but dividing them by the price coefficient, we get monetary values :
coef(ml.Train)[-1]/coef(ml.Train)[1]

#Mixed logit
Tr <- mlogit.data(Train, shape = "wide", varying = 4:11, choice = "choice", sep = "", opposite = c("price", "time", "change", "comfort"), alt.levels = c("choice1", "choice2"), id = "id")

Train.ml <- mlogit(choice ~ price + time + change + comfort, Tr)
summary(Train.ml)

Train.mxlc <- mlogit(choice ~ price + time + change + comfort, Tr, panel = TRUE, rpar = c(time = "cn", change = "n", comfort = "ln"), correlation = TRUE, R = 100, halton = NA)

summary(Train.mxlc)

Train.mxlu <- update(Train.mxlc, correlation = FALSE)


```



### Conditional Logit
Try with my data

Format data with demographic information using Tidyr.
To make a unique row for each observation including demographic data
I added column obs1-obs24 in excel.

These are columns 69-92 in cer_2016_01_08_dem2.csv
```{r}
ce_d <- read.csv("cer_2016_01_08_dem2.csv")
#str(ce_d)
#head(ce_d)
dem_long <- tidyr::gather(ce_d, "obs", "obs1_24", 69:92)
#str(dem_long)
#summary(dem_long$ID)
#View(dem_long)
# 9624 observations

#I deleted NAs in excel

write.csv(dem_long, "dem_long.csv")
```
I copied and pasted the demographic data from dem_long.csv into dswf_ml_dem2.csv

### Multinomial logit model
```{r}
wfml_d <- read.csv("dswf_ml_dem2.csv")

wfml_d2 <- mlogit.data(wfml_d, shape = "long", choice = "choice",
                     varying = 16:28, sep = "",
                     alt.levels = c(1, 2, 3), 
                     alt.var = "ALT", id = "id")
head(wfml_d2, 3)

ml.wfml <- mlogit(choice ~ small.loss + small.gain + big.gain + 
                    municipal + private + cooperative +  mi4 + mi8 +
                    mi10 + bill  | -1, wfml_d2)

summary(ml.wfml)

#these outputs are the same as when I used support.CEs package

#divide by bill coefficient to obtain WTP associated with each attribute and level
coef(ml.wfml)[-1]/coef(ml.wfml)[10]
```

Explore with all demographic variables

```{r}
ml.wfml.dem1 <- mlogit(choice ~ small.loss + small.gain + big.gain
              + municipal + private + cooperative +  mi4 + mi8 + 
                mi10 + bill + bill:income | -1, wfml_d2)

summary(ml.wfml.dem1)

test1 <- mlogit(choice ~ 1| small.loss + small.gain + big.gain + 
                    municipal + private + cooperative +  mi4 + mi8 +
                    mi10 + bill, wfml_d2, shape ="long", chid.var="id",
                    alt.var="alt", method = "bfgs", heterosc = TRUE,
                    tol=10)

test1 <- mlogit(choice ~ small.loss + small.gain + big.gain + 
                    municipal + private + cooperative +  mi4 + mi8 +
                    mi10 + bill | 1, wfml_d2, shape ="long", chid.var="id",
                    alt.var="ALT", method = "bfgs", heterosc = TRUE,
                    tol=10)
```

```{r}
summary(ml.wfml.dem1)
```

Building models with demographic variables added, one by one. 

```{r}
ml.wfml.dem <- mlogit(choice ~ small.loss + small.gain + big.gain +
                        municipal + private + cooperative +  
                        mi4 + mi8 + mi10 + bill + 
                        age:big.gain + female:big.gain +
                        white:big.gain + univ_degr:big.gain + 
                        income:big.gain + wages:big.gain + 
                        self.emp:big.gain + pol_dem:big.gain + 
                        pol_ind:big.gain + pol_rep:big.gain + 
                        coast_rec:big.gain
                      | 1, wfml_d2)


summary(ml.wfml.dem)
```
white
female
age
univ_degr
income
wages
self.emp
pol_dem
pol_ind
pol_rep
coast_rec




### Mixed Logit

```{r}
wf.mxlc <- mlogit(choice ~ small.loss + small.gain + big.gain + 
                    municipal + private + cooperative +  
                    mi4 + mi8 + mi10 + bill,
                  wfml2, panel = TRUE, rpar = c(small.loss = "n", small.gain = "n", big.gain = "n", municipal = "n", private = "n", cooperative = "n", mi4 = "n", mi8 = "n", mi10 = "n", bill = "n"), correlation = TRUE, R = 100, halton = NA)

summary(wf.mxlc)
```
Ai
```{r}
wf.mxlc2 <- mlogit(choice ~ small.loss + small.gain + big.gain + 
                    municipal + private + cooperative +  
                    mi4 + mi8 + mi10 + bill,
                  wfml2, panel = TRUE, rpar = c(small.loss = "n", small.gain = "n", big.gain = "n", municipal = "n", private = "n", cooperative = "n", mi4 = "n", mi8 = "n", mi10 = "n", bill = "n"), R = 100)

summary(wf.mxlc2)
```
What does panel do?

```{r}
#takes 10 min to run with no panel
wf.mxlc.np <- mlogit(choice ~ small.loss + small.gain + big.gain + 
                    municipal + private + cooperative +  
                    mi4 + mi8 + mi10 + bill,
                  wfml2, panel = FALSE, rpar = c(small.loss = "n", small.gain = "n", big.gain = "n", municipal = "n", private = "n", cooperative = "n", mi4 = "n", mi8 = "n", mi10 = "n", bill = "n"), correlation = TRUE, R = 100, halton = NA)
```

summary(wf.mxlc.np)
# not correlated
wf.mxlu <- update(wf.mxlc, correlation = FALSE)
summary(wf.mxlu)
```

Translate to dollar values
Normalize with bill 
```{r}
big.gain.value <- rpar(wf.mxlc, "big.gain", norm = "bill")
summary(big.gain.value)
med(big.gain.value)
mean(big.gain.value)

big.gain.value.nc <- rpar(wf.mxlu, "big.gain", norm = "bill")
summary(big.gain.value.nc)
med(big.gain.value.nc)
mean(big.gain.value.nc)
```

Use AIC to compare models

Interact with demographics 
e.g., age:mi4

goodness of fit
lrtest
AIC

demographics
test to see if panel = true or false, see how output differs

find best “base” model based on AIC and lrtest


