---
title: "Subset by demographic characteristics"
author: "Sarah Klain"
date: "May 6, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---
title: "Tidier Multinomial Logit"
author: "Sarah Klain"
date: "February 11, 2016"
output:
  pdf_document: default
  html_document:
    keep_md: yes
---


```{r}
setwd("/Users/sarahklain/Documents/R_2015/wf_ce/CE/demog")

#install.packages("support.CEs")
library(ggplot2)
library(ggthemes)
library(viridis)
suppressMessages(library(dplyr))
library(knitr)
library(tidyr)
library(broom)
#library(support.CEs)
library(survival)
library(mlogit)
library(stargazer)
```

### Conditional Logit

Format data with demographic information using Tidyr.
To make a unique row for each observation including demographic data
I added column obs1-obs24 in excel.

These are columns 69-92 in cer_2016_01_08_dem2.csv
```{r}
ce_d <- read.csv("cer_2016_01_08_dem2.csv")
ce_d_s <- summary(ce_d[11:20])
summary(ce_d)
# knitr:: kable(ce_d_s, align = 'c', format = 'markdown', digits = 4)
```

Subsample

```{r}
# Parameters
target_mean = .51
target_std = .5
subsample_size= 300
num_subsamples_to_keep = 5
num_subsamples_to_try = 10000

# This scoring metric is kind of arbitrary and could be tuned. 
# For this one, I'm giving equal penalty to deviations from the target mean and the 
# target standard deviation. If fitting the target mean was twice as important as 
# fitting the target std, you could use:
#    return(2*abs(mean-target_mean) + abs(std-target_std))
# Lower scores are better than higher scores. If you redefined the scoring function 
# to make high scores better, then you would need to do a reverse sort in the for loop below. 

calculate_score <- function(mean, target_mean, std, target_std) { 
    return(abs(mean-target_mean) + abs(std-target_std))
}

# Make up some data. This will have a different distribution than what we are looking for.
df = ce_d
#df = data.frame(x=rnorm(100), y=rnorm(100))

# The matrix saved_subsamples will stores the best subsamples, but it will start off blank.
# A corresponding dataframe below will store the scores (subsample_metrics). 
# We'll keep saved_subsamples and subsample_metrics synchronized so that row 1 in one 
# always corresponds to row 1 of the other. 
saved_subsamples = matrix(nrow=num_subsamples_to_keep, ncol=subsample_size)

# Store the metrics of a subsample's quality in this data frame. 
# We'll keep the rows of this synchronized with saved_subsamples and
# keep them both sorted so the worst saved subsample is always in the last row
# When we find a new subsample that's better than the worst known, we'll save 
# it and resort the matrix and dataframe.
subsample_metrics = data.frame(mean=matrix(NaN, nrow=num_subsamples_to_keep), std=matrix(NaN, nrow=num_subsamples_to_keep), score=matrix(NaN, nrow=num_subsamples_to_keep))

# Try a bunch of different subsamples and keep the best ones
for (attempt in 1:num_subsamples_to_try) {
    # Pick a new subsample and evaluate it. 
    subsample = sample(nrow(df$female),size=subsample_size)
  #subsample = sample(nrow(df),size=subsample_size)
    subsample_mean = mean(df$female[subsample,'x'])
    subsample_std = sd(df$female[subsample,'x'])
    subsample_score = calculate_score(subsample_mean, target_mean, subsample_std, target_std)
    # If we don't have any subsamples yet (worst score is NA), or if this new 
    # subsample is better than our worst saved subsample, then overwrite our 
    # worst subsample from the end and re-order the lists. 
    if( is.na(subsample_metrics[nrow(subsample_metrics),'score']) ||
            subsample_score < subsample_metrics[nrow(subsample_metrics),'score'] ) {
        # Overwrite the worst saved subsample (row 1)
        subsample_metrics[nrow(subsample_metrics),'mean'] = subsample_mean
        subsample_metrics[nrow(subsample_metrics),'std'] = subsample_std
        subsample_metrics[nrow(subsample_metrics),'score'] = subsample_score
        # Transpose the subsample so it fits in one row instead of one column
        saved_subsamples[nrow(saved_subsamples),] = t(subsample)
        # Reorder the saved subsamples (and corresponding metrics) so the worst 
        # scores (the largest) are at the bottom of the list.
        new_order = order(subsample_metrics$score)
        saved_subsamples = saved_subsamples[new_order,]
        subsample_metrics = subsample_metrics[new_order,]
    }
}

# Look at the top subsamples found & their scores
print(subsample_metrics)
print(saved_subsamples)

# Retrieve the top-scoring subsample from the end of the list
top_subsample_indexes = saved_subsamples[1,]
# Use that to subsample the original dataset
top_subsample = df[top_subsample_indexes,]
```

```{r}

#str(ce_d)
#head(ce_d)
dem_long <- tidyr::gather(ce_d, "obs", "obs1_24", 69:92)
#str(dem_long)
#summary(dem_long$ID)
#View(dem_long)
# 9624 observations

#I deleted NAs in excel

# write.csv(dem_long, "dem_long.csv")
```
I copied and pasted the demographic data from dem_long.csv into dswf_ml_dem2.csv

Make table of variable means
```{r}
wfml_d <- read.csv("dswf_ml_dem2.csv")
w_tbl <- tbl_df(wfml_d)
  
# tbl2 <- dplyr::select(w_tbl, ASC: coast_rec)
# View(tbl2)

# tbl3 <- dplyr::summarise_each(tbl2, funs(mean))

# knitr:: kable(tbl3, align = 'c', format = 'markdown', digits = 4)

```

### Multinomial logit model

```{r}
wfml_d <- read.csv("dswf_ml_dem2.csv")

wfml_d2 <- mlogit.data(wfml_d, shape = "long", choice = "choice",
                     varying = 16:28, sep = "",
                     alt.levels = c(1, 2, 3), 
                     alt.var = "ALT", id = "id")
# head(wfml_d2, 3)

ml.bl.st.mi1 <- mlogit(choice ~ small.loss + small.gain + big.gain + 
                    municipal + private + cooperative +  mi4 + mi8 +
                    mi10 + bill  | -1, wfml_d2)

summary(ml.bl.st.mi1)
-1 * coef(ml.bl.st.mi1)[1:10]/coef(ml.bl.st.mi1)[10]
AIC(ml.bl.st.mi1)

#these outputs are the same as when I used support.CEs package
#from Croissant: coef(ml.Train)[-1]/coef(ml.Train)[1]
#divide by bill coefficient to obtain WTP associated with each attribute and level

#calc confidence intervals for WTP
# Exponeniate to make these confidence intervals for the odds ratio 
exp(confint(ml.bl.st.mi1))

```


Explore with demographic variables

```{r}
ml.bl.st.mi1.dem <- mlogit(choice ~ small.loss + small.gain +
                        big.gain + 
                        municipal + private +                  
                        cooperative +  
                        mi4 + mi8 + mi10 + bill + 
                        age:ASC + female:ASC +
                        white:ASC + univ_degr:ASC + 
                        income:ASC + wages:ASC + 
                        self.emp:ASC + pol_dem:ASC + 
                        pol_ind:ASC + pol_rep:ASC + 
                        coast_rec:ASC
                      | 1, wfml_d2)

summary(ml.bl.st.mi1.dem)


coef(ml.bl.st.mi1.dem)[1:21]/coef(ml.bl.st.mi1.dem)[12]
AIC(ml.bl.st.mi1.dem)

ml.bl.pr.mi1.dem2 <- mlogit(choice ~ small.loss + small.gain +
                        big.gain + 
                        municipal + state +                  
                        cooperative +  
                        mi4 + mi8 + mi10 + bill + 
                        age:ASC + female:ASC +
                        white:ASC + univ_degr:ASC +
                        coast_rec:ASC
                      | 1, wfml_d2)

summary(ml.bl.pr.mi1.dem2)
AIC(ml.bl.pr.mi1.dem2)

coef(ml.bl.pr.mi1.dem2)[1:21]/coef(ml.bl.pr.mi1.dem2)[12]

```


```{r}
ml.bl.pr.mi1.dem.bg.a.f <- mlogit(choice ~ small.loss + small.gain +
                        big.gain + 
                        municipal + state +                  
                        cooperative +  
                        mi4 + mi8 + mi10 + bill + 
                        age:big.gain + female:big.gain
                      | 1, wfml_d2)

summary(ml.bl.pr.mi1.dem.bg.a.f)
AIC(ml.bl.pr.mi1.dem.bg.a.f)
```


```{r}
ml.bl.pr.mi1.dem3 <- mlogit(choice ~ small.loss + small.gain +
                        big.gain + 
                        municipal + state +                  
                        cooperative +  
                        mi4 + mi8 + mi10 + bill + 
                        age:ASC + female:ASC +
                        white:ASC + univ_degr:ASC + 
                        income:ASC +
                        self.emp:ASC + pol_dem:ASC + 
                        pol_ind:ASC + pol_rep:ASC 
                       + coast_rec:ASC +  
                        oper:ASC + const_st:ASC +
                        wf_rec:ASC+ 
                        abuse_nep:ASC + bal_r_nep:ASC + 
                        crisis_r_nep:ASC + spaceship_nep:ASC +
                      # bau_nep:ASC +
                     # extract_r_ins:ASC +
                      # loss_r_ins:ASC + decade_r_mor:ASC 
                      # comm_rel:ASC + wild_rel:ASC +
                    # clean_inst:ASC + tech:ASC + 
                      iden_rel:ASC + kin_rel:ASC + 
                        right_r_mor:ASC + health_rel:ASC + 
                        other_rel:ASC + kin_met:ASC + 
                        resp_met:ASC + iden_met:ASC + 
                        other_met:ASC
                      | 1, wfml_d2)

summary(ml.bl.pr.mi1.dem3)
-1 * coef(ml.bl.pr.mi1.dem3)[1:21]/coef(ml.bl.pr.mi1.dem3)[12]
AIC(ml.bl.pr.mi1.dem3)
```


```{r}
ml.bl.pr.mi1.dem4 <- mlogit(choice ~ small.loss + small.gain +
                        big.gain + 
                        municipal + state +                  
                        cooperative +  
                        mi4 + mi8 + mi10 + bill + 
                        age:ASC + female:ASC +
                        white:ASC + univ_degr:ASC + 
                        income:ASC +
                        pol_dem:ASC + pol_ind:ASC + pol_rep:ASC 
                       + coast_rec:ASC + mean_nep:ASC + 
                        oper:ASC + wf_rec:ASC+ other_met:ASC
                      | 1, wfml_d2)

summary(ml.bl.pr.mi1.dem4)
AIC(ml.bl.pr.mi1.dem4)
```

```{r}
ml.bl.pr.mi1.dem5 <- mlogit(choice ~ small.loss + small.gain +
                        big.gain + 
                        municipal + state +                  
                        cooperative +  
                        mi4 + mi8 + mi10 + bill + 
                        age:ASC + female:ASC +
                        white:ASC + univ_degr:ASC + 
                        income:ASC +
                        self.emp:ASC + pol_dem:ASC + 
                        pol_ind:ASC + pol_rep:ASC 
                       + coast_rec:ASC + mean_nep:ASC + 
                        oper:ASC + const_st:ASC +
                        wf_rec:ASC+ crisis_r_nep:ASC + spaceship_nep:ASC +
                        right_r_mor:ASC + health_rel:ASC + 
                        other_rel:ASC + kin_met:ASC + iden_met:ASC + 
                        other_met:ASC
                      | 1, wfml_d2)

summary(ml.bl.pr.mi1.dem5)
AIC(ml.bl.pr.mi1.dem5)
```

```{r}
ml.bl.pr.mi1.dem6 <- mlogit(choice ~ small.loss + small.gain +
                        big.gain + 
                        municipal + state +                  
                        cooperative +  
                        mi4 + mi8 + mi10 + bill + 
                        age:ASC + female:ASC +
                        white:ASC + univ_degr:ASC + 
                        income:ASC + coast_rec:ASC 
                        + oper:ASC + const_st:ASC +
                        wf_rec:ASC
                      | 1, wfml_d2)

summary(ml.bl.pr.mi1.dem6)
AIC(ml.bl.pr.mi1.dem6)
```


### Mixed Logit

```{r}
#mixed logits take ~5 min to run

mx.bl.pr.mi1 <- mlogit(choice ~ small.loss + small.gain + big.gain + 
                    municipal + state + cooperative +  
                    mi4 + mi8 + mi10 + bill,
                  wfml_d2, panel = TRUE, rpar = c(small.loss = "n", small.gain = "n", big.gain = "n", municipal = "n", state = "n", cooperative = "n", mi4 = "n", mi8 = "n", mi10 = "n", bill = "n"), correlation = TRUE, R = 100, halton = NA)

summary(mx.bl.pr.mi1)
-1 * (coef(mx.bl.pr.mi1)[3:12]/coef(mx.bl.pr.mi1)[12])
AIC(mx.bl.pr.mi1)
exp(confint(mx.bl.pr.mi1))
```

```{r}
mx.bl.pr.mi1.dem <- mlogit(choice ~ small.loss + small.gain + big.gain + 
                    municipal + state + cooperative +  
                    mi4 + mi8 + mi10 + bill 
                    + age:ASC + female:ASC + white:ASC + univ_degr:ASC + 
                        income:ASC + coast_rec:ASC + oper:ASC + const_st:ASC +
                        wf_rec:ASC,
                  wfml_d2, panel = TRUE, rpar = c(small.loss = "n", small.gain = "n", big.gain = "n", municipal = "n", state = "n", cooperative = "n", mi4 = "n", mi8 = "n", mi10 = "n", bill = "n"), correlation = TRUE, R = 100, halton = NA)

summary(mx.bl.pr.mi1.dem)
#-1 * ((mx.bl.pr.mi1.dem)[3:12]/coef(mx.bl.pr.mi1.dem)[12])
AIC(mx.bl.pr.mi1.dem)
```

```{r}
mx.bl.pr.mi1.dem2 <- mlogit(choice ~ small.loss + small.gain + big.gain + 
                    municipal + state + cooperative +  
                    mi4 + mi8 + mi10 + bill 
                    + age:big.gain + female:big.gain + white:big.gain + univ_degr:big.gain
                    + income:big.gain + coast_rec:big.gain + oper:big.gain + 
                      const_st:big.gain + wf_rec:big.gain,
                  wfml_d2, panel = TRUE, rpar = c(small.loss = "n", small.gain = "n", big.gain = "n", municipal = "n", state = "n", cooperative = "n", mi4 = "n", mi8 = "n", mi10 = "n", bill = "n"), correlation = TRUE, R = 100, halton = NA)

summary(mx.bl.pr.mi1.dem2)
#-1 * coef((mx.bl.pr.mi1.dem2)[3:12]/coef(mx.bl.pr.mi1.dem2)[12])
AIC(mx.bl.pr.mi1.dem2)

```

```{r}
mx.bl.pr.mi1.dem3 <- mlogit(choice ~ small.loss + small.gain + big.gain + 
                    municipal + state + cooperative +  
                    mi4 + mi8 + mi10 + bill 
                    + age:big.gain + female:big.gain + white:big.gain + univ_degr:big.gain
                    + income:big.gain + coast_rec:big.gain,
                  wfml_d2, panel = TRUE, rpar = c(small.loss = "n", small.gain = "n", big.gain = "n", municipal = "n", state = "n", cooperative = "n", mi4 = "n", mi8 = "n", mi10 = "n", bill = "n"), correlation = TRUE, R = 100, halton = NA)

summary(mx.bl.pr.mi1.dem3)
#-1 * (coef(mx.bl.pr.mi1.dem3)[3:12]/coef(mx.bl.pr.mi1.dem3)[12])

AIC(mx.bl.pr.mi1.dem3)


```

Translate to dollar values
Normalize with bill 
```{r}
# big.gain.value <- rpar(wf.mxlc, "big.gain", norm = "bill")
# summary(big.gain.value)
# med(big.gain.value)
# mean(big.gain.value)
```

Use AIC to compare models
```{r}
AIC(ml.bl.st.mi1)
AIC(ml.bl.pr.m1)
AIC(ml.sl.pr.m1)
AIC(ml.sg.st.mi1)
AIC(ml.bl.st.mi1.dem)
AIC(ml.bl.pr.mi1.dem2)
AIC(ml.bl.pr.mi1.dem2)
AIC(ml.bl.pr.mi1.dem3)
AIC(ml.bl.pr.mi1.dem5)
AIC(ml.bl.pr.mi1.dem6)
AIC(mx.bl.st.mi1)
AIC(mx.bl.pr.mi1)
AIC(mx.bl.pr.mi1.dem)
```

Likelihood Ratio Test

```{r}
# lrtest(ml.bl.pr.mi1.dem6, ml.bl.pr.mi1.dem2)
```

Interact with demographics 
e.g., age:mi4

goodness of fit
lrtest
AIC

demographics
test to see if panel = true or false, see how output differs
find best “base” model based on AIC and lrtest


```{r}
setwd("/Users/sarahklain/Documents/R_2015/wf_ce/CE/mlogit/")
wtp <- read.csv("model_r.csv")

wtp$attribute <- factor(wtp$attribute, levels=c( "4 miles", "8 miles", "10 miles",  "municipal", "state", "coop","small loss", "small gain", "big gain"))

bar_wtp <- ggplot(wtp, aes(x = attribute, y = WTP, fill = attribute)) +
  geom_bar(stat = "identity") +
  scale_fill_viridis(discrete=TRUE, option = "viridis") +
  xlab("Offshore Wind Farm Attributes") +
  ylab("WTP ($/month)") +
  ggtitle("Willingness to pay for offshore wind farm attributes") +
  theme(legend.position = "none")

bar_wtp

ggsave("wtp.pdf", width = 6, height = 4)
```

