---
title: "Tidier Multinomial Logit"
author: "Sarah Klain"
date: "February 11, 2016"
output:
  pdf_document: default
  html_document:
    keep_md: yes
---

---
title: "CE_mlogit"
author: "Sarah Klain"
date: "November 20, 2015"
output: 
  html_document: 
    keep_md: yes
---

```{r}
setwd("/Users/sarahklain/Documents/R_2015/wf_ce/CE/demog")

#install.packages("support.CEs")
library(ggplot2)
library(ggthemes)
library(viridis)
suppressMessages(library(dplyr))
library(knitr)
library(tidyr)
library(broom)
#library(support.CEs)
library(survival)
library(mlogit)
library(stargazer)
```

### Conditional Logit

Format data with demographic information using Tidyr.
To make a unique row for each observation including demographic data
I added column obs1-obs24 in excel.

These are columns 69-92 in cer_2016_01_08_dem2.csv
```{r}
ce_d <- read.csv("cer_2016_01_08_dem2.csv")
ce_d_s <- summary(ce_d[11:20])
knitr:: kable(ce_d_s, align = 'c', format = 'markdown', digits = 4)
  
#str(ce_d)
#head(ce_d)
dem_long <- tidyr::gather(ce_d, "obs", "obs1_24", 69:92)
#str(dem_long)
#summary(dem_long$ID)
#View(dem_long)
# 9624 observations

#I deleted NAs in excel

write.csv(dem_long, "dem_long.csv")
```
I copied and pasted the demographic data from dem_long.csv into dswf_ml_dem2.csv

Make table of variable means
```{r}
wfml_d <- read.csv("dswf_ml_dem2.csv")
w_tbl <- tbl_df(wfml_d)
  
tbl2 <- dplyr::select(w_tbl, ASC: coast_rec)
View(tbl2)

tbl3 <- dplyr::summarise_each(tbl2, funs(mean))

knitr:: kable(tbl3, align = 'c', format = 'markdown', digits = 4)

```

tmp <- do.call(data.frame, 
           list(mean = apply(test, 2, mean),
                sd = apply(test, 2, sd),
                median = apply(test, 2, median),
                min = apply(test, 2, min),
                max = apply(test, 2, max),
                n = apply(test, 2, length)))
tmp
```


### Multinomial logit model
```{r}
wfml_d <- read.csv("dswf_ml_dem2.csv")

wfml_d2 <- mlogit.data(wfml_d, shape = "long", choice = "choice",
                     varying = 16:28, sep = "",
                     alt.levels = c(1, 2, 3), 
                     alt.var = "ALT", id = "id")
head(wfml_d2, 3)

ml.wfml <- mlogit(choice ~ small.loss + small.gain + big.gain + 
                    municipal + private + cooperative +  mi4 + mi8 +
                    mi10 + bill  | -1, wfml_d2)

summary(ml.wfml)

#these outputs are the same as when I used support.CEs package

#from Croissant: coef(ml.Train)[-1]/coef(ml.Train)[1]
#divide by bill coefficient to obtain WTP associated with each attribute and level

#I am confused by negative number of WTP
coef(ml.wfml)[-3]/coef(ml.wfml)[10]

coef(ml.wfml)[-4]/coef(ml.wfml)[10]

coef(ml.wfml)[1:10]/coef(ml.wfml)[10]

#calc confidence intervals for WTP
#return to this later

```

Explore with demographic variables

```{r}
ml.wfml.dem2 <- mlogit(choice ~ small.loss + small.gain +
                        big.gain + 
                        municipal + private +                  
                        cooperative +  
                        mi4 + mi8 + mi10 + bill + 
                        age:ASC + female:ASC +
                        white:ASC + univ_degr:ASC + 
                        income:ASC + wages:ASC + 
                        self.emp:ASC + pol_dem:ASC + 
                        pol_ind:ASC + pol_rep:ASC + 
                        coast_rec:ASC
                      | 1, wfml_d2)

summary(ml.wfml.dem2)

#stargazer(ml.wfml.dem2, type = "text")
knitr:: kable(ml.wfml.dem2, align = 'c', format = 'markdown', digits = 4)

coef(ml.wfml.dem2)[1:21]/coef(ml.wfml.dem2)[12]

```



```{r}
ml.wfml.dem3 <- mlogit(choice ~ small.loss + small.gain +
                        big.gain + 
                        municipal + private +                  
                        cooperative +  
                        mi4 + mi8 + mi10 + bill + 
                        age:ASC + female:ASC +
                        white:ASC + univ_degr:ASC + 
                        income:ASC +
                        self.emp:ASC + pol_dem:ASC + 
                        pol_ind:ASC + pol_rep:ASC 
                       + coast_rec:ASC + mean_nep:ASC + 
                        oper:ASC + const_st:ASC +
                        wf_rec:ASC+ app:ASC + 
                        abuse_nep:ASC + bal_r_nep:ASC + 
                        crisis_r_nep:ASC + spaceship_nep:ASC +
                      # bau_nep:ASC +
                     # extract_r_ins:ASC +
                      # loss_r_ins:ASC + decade_r_mor:ASC 
                      # comm_rel:ASC + wild_rel:ASC +
                    # clean_inst:ASC + tech:ASC + tech_r:ASC + 
                      iden_rel:ASC + kin_rel:ASC + 
                        right_r_mor:ASC + health_rel:ASC + 
                        other_rel:ASC + kin_met:ASC + 
                        resp_met:ASC + iden_met:ASC + 
                        other_met:ASC
                      | 1, wfml_d2)

summary(ml.wfml.dem3)
```


```{r}
ml.wfml.dem5 <- mlogit(choice ~ small.loss + small.gain +
                        big.gain + 
                        municipal + private +                  
                        cooperative +  
                        mi4 + mi8 + mi10 + bill + 
                        age:ASC + female:ASC +
                        white:ASC + univ_degr:ASC + 
                        income:ASC +
                         pol_dem:ASC + pol_ind:ASC + pol_rep:ASC 
                       + coast_rec:ASC + mean_nep:ASC + 
                        oper:ASC + wf_rec:ASC+ other_met:ASC
                      | 1, wfml_d2)

summary(ml.wfml.dem5)
```

```{r}
ml.wfml.dem6 <- mlogit(choice ~ small.loss + small.gain +
                        big.gain + 
                        municipal + private +                  
                        cooperative +  
                        mi4 + mi8 + mi10 + bill + 
                        age:ASC + female:ASC +
                        white:ASC + univ_degr:ASC + 
                        income:ASC +
                        self.emp:ASC + pol_dem:ASC + 
                        pol_ind:ASC + pol_rep:ASC 
                       + coast_rec:ASC + mean_nep:ASC + 
                        oper:ASC + const_st:ASC +
                        wf_rec:ASC+ app:ASC + crisis_r_nep:ASC + spaceship_nep:ASC +
                        right_r_mor:ASC + health_rel:ASC + 
                        other_rel:ASC + kin_met:ASC + iden_met:ASC + 
                        other_met:ASC
                      | 1, wfml_d2)

summary(ml.wfml.dem6)
```

### Mixed Logit

```{r}
wf.mxlc <- mlogit(choice ~ small.loss + small.gain + big.gain + 
                    municipal + private + cooperative +  
                    mi4 + mi8 + mi10 + bill,
                  wfml_d2, panel = TRUE, rpar = c(small.loss = "n", small.gain = "n", big.gain = "n", municipal = "n", private = "n", cooperative = "n", mi4 = "n", mi8 = "n", mi10 = "n", bill = "n"), correlation = TRUE, R = 100, halton = NA)

summary(wf.mxlc)
```
Ai
```{r}
wf.mxlc2 <- mlogit(choice ~ small.loss + small.gain + big.gain + 
                    municipal + private + cooperative +  
                    mi4 + mi8 + mi10 + bill,
                  wfml_d2, panel = TRUE, rpar = c(small.loss = "n", small.gain = "n", big.gain = "n", municipal = "n", private = "n", cooperative = "n", mi4 = "n", mi8 = "n", mi10 = "n", bill = "n"), R = 100)

summary(wf.mxlc2)
```
What does panel do?

### ```{r}
### takes 10 min to run with no panel
wf.mxlc.np <- mlogit(choice ~ small.loss + small.gain + big.gain + 
                    municipal + private + cooperative +  
                    mi4 + mi8 + mi10 + bill,
                  wfml2, panel = FALSE, rpar = c(small.loss = "n", small.gain = "n", big.gain = "n", municipal = "n", private = "n", cooperative = "n", mi4 = "n", mi8 = "n", mi10 = "n", bill = "n"), correlation = TRUE, R = 100, halton = NA)
### ```

summary(wf.mxlc.np)

### not correlated
```{r}
wf.mxlu <- update(wf.mxlc, correlation = FALSE)
summary(wf.mxlu)
```

```

Translate to dollar values
Normalize with bill 
```{r}
big.gain.value <- rpar(wf.mxlc, "big.gain", norm = "bill")
summary(big.gain.value)
med(big.gain.value)
mean(big.gain.value)

big.gain.value.nc <- rpar(wf.mxlu, "big.gain", norm = "bill")
summary(big.gain.value.nc)
med(big.gain.value.nc)
mean(big.gain.value.nc)
```

Use AIC to compare models
```{r}
AIC(ml.wfml)
AIC(ml.wfml.dem2)
AIC(ml.wfml.dem3)
AIC(ml.wfml.dem5)
AIC(ml.wfml.dem6)
AIC(wf.mxlu)
AIC(wf.mxlc2)
```

Likelihood Ratio Test

```{r}
lrtest(ml.wfml, wf.mxlu)
```




Interact with demographics 
e.g., age:mi4

goodness of fit
lrtest
AIC

demographics
test to see if panel = true or false, see how output differs
find best “base” model based on AIC and lrtest


